|

### 2021-03-17 documentation/readme.Rmd
Update README images and text

timeplot <- 
pollbasepro %>% 
  pivot_longer(
    cols = c(-date, -election, -govt, -week, -month, -quarter, -year, -con_ldr, -lab_ldr, -lib_ldr),
    names_to = c("party", ".value"),
    names_sep = "_",
  ) %>%
  mutate(
    party =
      case_when(
        party == "con" ~ "Conservative Party",
        party == "lab" ~ "Labour Party",
        party == "lib" ~ "Liberals (Various Forms)"
      ) %>% 
      factor(
        levels = 
          c("Conservative Party",
            "Labour Party",
            "Liberals (Various Forms)"
          )
      )
  ) %>%
  ggplot(
    aes(
      x = date,
      y = est,
      ymin = est - qnorm(0.975)*err,
      ymax = est + qnorm(0.975)*err,
      colour = party,
      fill = party
    )
  ) +
  geom_ribbon(alpha = .3, colour = NA) +
  geom_line() +
  scale_colour_manual(values = pty_cols) +
  scale_fill_manual(values = pty_cols) +
  scale_y_continuous(
    breaks = seq(0, .6, by = .1),
    labels = scales::percent_format(accuracy = 1)
    ) +
  scale_x_date(
    breaks = seq.Date(as.Date("1955-01-01"), max(pollbasepro$date), by = "3 months"),
    labels = format(seq.Date(as.Date("1955-01-01"), max(pollbasepro$date), by = "3 months"), "%b %y")
    ) +
  coord_cartesian(
    ylim = c(0, 0.62),
    xlim = c(as_date("2019-12-12"), Sys.Date())
    ) +
  theme_minimal() +
    theme(
      legend.position = "bottom",
      legend.title = element_blank(),
      text = element_text(family = "Cabin", color = "black", size = 8),
      plot.title = element_text(family = "Cabin", face = "bold", size = rel(1.4), hjust = 0),
      plot.subtitle = element_text(family = "Cabin", size = rel(1), hjust = 0, margin = margin(b = 10)),
      axis.line = element_line(lineend = "round"),
      axis.title.x = element_blank(),
      axis.text.x = element_text(color = "black", size = rel(1)),
      axis.ticks.x = element_line(lineend = "round"),
      axis.title.y = element_text(family = "Cabin", face = "bold", size = rel(1)),
      axis.text.y = element_text(color = "black", size = rel(1)),
      strip.text = element_text(family = "Cabin", face = "bold", size = rel(1)),
      panel.spacing = unit(.3, "cm"),
      panel.grid.major.y = element_line(size = .5, lineend = "round"),
      panel.grid.minor.y = element_blank(),
      panel.grid.major.x = element_blank(),
      panel.grid.minor.x = element_blank()
    ) +
  labs(
    title = paste0("British Poll of Polls, ", str_remove(format(max(pollbasepro$date), "%d %B %Y"), "^0")),
    colour = "Party",
    fill = "Party",
    y = "Vote Share",
    caption = "Made using PollBasePro by @PoliSciJack, @markpack, and @mansillo"
  )

@@

ggsave(
  filename = "timeplot_gh.png",
  plot = timeplot,
  path = here("documentation", "_assets"),
  width = 3.5,
  height = 3.5,
  units = "in",
  dpi = 320
)

@@

- **`r txt_dta$party[1]`:** `r paste0(txt_dta$share[1], " (95% CI: ", txt_dta$lower[1], " to ", txt_dta$upper[1], ")")`
- **`r txt_dta$party[2]`:** `r paste0(txt_dta$share[2], " (95% CI: ", txt_dta$lower[2], " to ", txt_dta$upper[2], ")")`
- **`r txt_dta$party[3]`:** `r paste0(txt_dta$share[3], " (95% CI: ", txt_dta$lower[3], " to ", txt_dta$upper[3], ")")`

As of `r str_remove(format(max(pollbasepro$date), "%d %B %Y"), "^0")`, **the `r txt_dta$party[1]` `r ifelse(txt_dta$party[1] %in% c("Conservative Party", "Labour Party"), "is", "are")` the largest party**. **They hold a lead over the `r txt_dta$party[2]`** of `r paste0(scales::percent(txt_dta$est[1] - txt_dta$est[2]), " (95% CI: ", scales::percent((txt_dta$est[1] - txt_dta$est[2]) - qnorm(.975)*sqrt(txt_dta$err[1]^2 + txt_dta$err[2]^2)), " to ", scales::percent((txt_dta$est[1] - txt_dta$est[2]) + qnorm(.975)*sqrt(txt_dta$err[1]^2 + txt_dta$err[2]^2)), ")")`. **This puts the `r txt_dta$party[2]` in second place** and **the `r txt_dta$party[3]` in third place**.

>>>>

timeplot <- 
pollbasepro %>% 
  pivot_longer(
    cols = c(-date, -election, -govt, -week, -month, -quarter, -year, -con_ldr, -lab_ldr, -lib_ldr),
    names_to = c("party", ".value"),
    names_sep = "_",
  ) %>%
  mutate(
    party =
      case_when(
        party == "con" ~ "Conservative Party",
        party == "lab" ~ "Labour Party",
        party == "lib" ~ "Liberals (Various Forms)"
      ) %>% 
      factor(
        levels = 
          c("Conservative Party",
            "Labour Party",
            "Liberals (Various Forms)"
          )
      )
  ) %>%
  ggplot(
    aes(
      x = date,
      y = est,
      ymin = est - qnorm(0.975)*err,
      ymax = est + qnorm(0.975)*err,
      colour = party,
      fill = party
    )
  ) +
  geom_ribbon(alpha = .3, colour = NA) +
  geom_line() +
  scale_colour_manual(values = pty_cols) +
  scale_fill_manual(values = pty_cols) +
  scale_y_continuous(
    breaks = seq(0, .6, by = .1),
    labels = scales::percent_format(accuracy = 1)
    ) +
  scale_x_date(
    breaks = seq.Date(as.Date("1955-01-01"), max(pollbasepro$date), by = "3 months"),
    labels = format(seq.Date(as.Date("1955-01-01"), max(pollbasepro$date), by = "3 months"), "%b %y")
    ) +
  coord_cartesian(
    ylim = c(0, 0.62),
    xlim = c(as_date("2019-12-12"), Sys.Date())
    ) +
  theme_minimal() +
    theme(
      legend.position = "none",
      legend.title = element_blank(),
      text = element_text(family = "Cabin", color = "black", size = 8),
      plot.title = element_blank(),
      plot.subtitle = element_text(family = "Cabin", size = rel(1), hjust = 0, margin = margin(b = 10)),
      axis.line = element_line(lineend = "round"),
      axis.title.x = element_blank(),
      axis.text.x = element_text(color = "black", size = rel(1)),
      axis.ticks.x = element_line(lineend = "round"),
      axis.title.y = element_text(family = "Cabin", face = "bold", size = rel(1)),
      axis.text.y = element_text(color = "black", size = rel(1)),
      strip.text = element_text(family = "Cabin", face = "bold", size = rel(1)),
      panel.spacing = unit(.3, "cm"),
      panel.grid.major.y = element_line(size = .5, lineend = "round"),
      panel.grid.minor.y = element_blank(),
      panel.grid.major.x = element_blank(),
      panel.grid.minor.x = element_blank()
    ) +
  labs(
    title = paste0("British Poll of Polls, ", str_remove(format(max(pollbasepro$date), "%d %B %Y"), "^0")),
    colour = "Party",
    fill = "Party",
    y = "Vote Share",
    caption = "Made using PollBasePro by @PoliSciJack, @markpack, and @mansillo"
  )

@@

ggsave(
  filename = "timeplot_gh.png",
  plot = timeplot,
  path = here("documentation", "_assets"),
  width = 3.5,
  height = 3,
  units = "in",
  dpi = 320
)

@@

- **`r txt_dta$party[1]`:** `r paste0(txt_dta$share[1], " (", txt_dta$lower[1], " to ", txt_dta$upper[1], ")")`
- **`r txt_dta$party[2]`:** `r paste0(txt_dta$share[2], " (", txt_dta$lower[2], " to ", txt_dta$upper[2], ")")`
- **`r txt_dta$party[3]`:** `r paste0(txt_dta$share[3], " (", txt_dta$lower[3], " to ", txt_dta$upper[3], ")")`

As of `r str_remove(format(max(pollbasepro$date), "%d %B %Y"), "^0")`, the `pollbasepro` model suggests that **the `r txt_dta$party[1]` `r ifelse(txt_dta$party[1] %in% c("Conservative Party", "Labour Party"), "is", "are")` the largest party** in Britain. **They hold a lead over the `r txt_dta$party[2]`** of `r paste0(scales::percent(txt_dta$est[1] - txt_dta$est[2]), " (95% CI: ", scales::percent((txt_dta$est[1] - txt_dta$est[2]) - qnorm(.975)*sqrt(txt_dta$err[1]^2 + txt_dta$err[2]^2)), " to ", scales::percent((txt_dta$est[1] - txt_dta$est[2]) + qnorm(.975)*sqrt(txt_dta$err[1]^2 + txt_dta$err[2]^2)), ")")`. **This puts the `r txt_dta$party[2]` in second place** and **the `r txt_dta$party[3]` in third place**.
